\tool: Revisiting BadUSB with Type-C

### 2021-03-04 WOOT/Files/experiment.tex
minor
fuck
move table
steps of desensitization in user study

	\caption{\tool Prototype}
	\label{fig:armory}
\end{figure}

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
		\hline
		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
		\hline
		\textbf{Total Number of Records} & \multicolumn{6}{c}{4172} \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Privacy Extraction Result}
	\label{table:information_extracted}
\end{table*}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
	\caption{Bar/QR Code Payment Procedure}
	\label{fig:qr_payment_procedure}
\end{figure}

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
After the case study experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

>>>>

	\caption{\tool Prototype.}
	\label{fig:armory}
\end{figure}

@@

\begin{table*}[t]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|}
		\hline
		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
		\hline
		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
		\hline
		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
		\hline
	\end{tabular}
	\linebreak
	\caption{Privacy Extraction Result.}
	\label{table:information_extracted}
\end{table*}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
	\caption{Bar/QR Code Payment Procedure.}
	\label{fig:qr_payment_procedure}
\end{figure}

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding OCR results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the OCR result with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized OCR result back to us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}
